Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

@@

Our second results deals with the disc-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disc and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disc-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii.
However, its strenght is not the same for all galaxies and strongly
correlates with halo triaxiality measured at $0.12R_{200}$.

>>>>

The halo shape also twists in the presence of baryons, as opposed to
the situation in DMO simulations where the shape is coherent as a
function of radius.
In Figure \ref{fig:alignment_correlations} we show the correlation
between twisting and the same baryonic properties that showd a high
degree of correlation with the triaxility.
In this case the disc to total ratio does not have a significant
degree of correlation.
Instead, the disc optical radius and the gas density at the core are
the most correlated. 
The correlation is such that extended stellar discs with a very low
gas density at its core show the most coherent halo shapes.

@@
